Using best practices for forecasting biodiversity changes in breeding birds

### 2017-07-28 manuscript/draft.Rmd
add figs to manuscript

Developing forecasts for biodiversity is important for conservation, management,
and evaluating how well current models characterize natural systems. While there
are an increasing number of studies forecasting biodiversity, there is little
information available on how well these forecasts work because these studies
fail to follow good practice for making and evaluating forecasts. Most diversity
forecasts do not conduct meaningful evaluations of the forecasts, fail to
account for uncertainty, and do not use time-series data that captures the
actual dynamics being studied. Using hindcasting we made and evaluated XXXX
[number of years * number of models * number of sites] forecasts for breeding
bird species richness at XXX sites throughout North America following best
practices for forecasting. Forecasts were made for up to a decade into the
future. Our results show that while all of the models we evaluated produce
reasonable forecasts, none of them outperforms the simple baseline of long-term
average richness. This means that at present our best forecast for future
richness is simply to assume that it is unchanging. This calls into question the
efficacy of current modeling approaches. Most of the best practices implemented
in this study directly influence the outcome of the forecasts and result in
different conclusions from those made in previous studies. This emphasizes the
importance of following good practice in making ecological forecasts and of
starting to actively make more forecasts in such a way that they can be quickly
evaluated and improved on.

@@

@@

@@

@@

>>>>

@@

![](../figures/model_predictions.png)

@@

![](../figures/scatter.png)

@@

![](../figures/model_violins.png)

![](../figures/performance_time.png)

@@

![](../figures/observers.png)
